
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}      % Critical for Mac BasicTeX
\usepackage{lmodern}          % Universal Vector Font (Guaranteed to exist)
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{textcomp}         % For currency symbols like $

% Define Colors
\definecolor{navy}{RGB}{10, 25, 60}
\definecolor{sentinelred}{RGB}{200, 30, 30}
\definecolor{grey}{RGB}{100, 100, 100}

% Custom commands
\newcommand{\sectionheader}[1]{{\large\textbf{\textcolor{navy}{#1}}}}

\title{\textbf{Sentinel Strategic Alert}}
\date{}

\begin{document}

% --- Header ---
\noindent
{\Huge \textbf{Sentinel Strategic Alert: \textcolor{navy}{vercel.com}}} \\
{\small \textcolor{grey}{Generated: 2026-02-05 00:17}}

\vspace{0.8cm}

% --- Verdict ---
\noindent
\colorbox{navy!10}{\parbox{\dimexpr\textwidth-2\fboxsep}{
    \vspace{2mm}
    \begin{center}
    \textbf{\textcolor{navy}{STRATEGIC ANALYSIS}}
    \end{center}
    \vspace{1mm}
    \noindent
    Pivot to Flexible Spending (Usage Credits) and Network Effect (Free Viewer Seats).
    \vspace{2mm}
}}

\vspace{1cm}

% --- Comparison Table ---
\renewcommand{\arraystretch}{1.5}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.46\textwidth}|>{\raggedright\arraybackslash}p{0.46\textwidth}@{}}
    \textbf{\large 6 Months Ago (Historical)} & \textbf{\large Today (Current)} \\
    \hline
    & \\[-0.5em]

    \sectionheader{TAGLINE} & \sectionheader{TAGLINE} \\
    Find a plan to power your apps. & Find a plan to power your apps. \\[0.5em]

    \sectionheader{AUDIENCE} & \sectionheader{AUDIENCE} \\
    Personal/non-commercial (Hobby), small teams with moderate usage (Pro), or large teams needing critical security, performance, and advanced support (Enterprise). & Personal users (Hobby), professional developers, freelancers, businesses (Pro), and enterprises requiring critical security, performance, and advanced support. \\[0.5em]

    \sectionheader{PRICING} & \sectionheader{PRICING} \\
    \textbf{Hobby} (Free forever) \newline {\footnotesize 1M Edge Requests, 100GB Fast Data Transfer, 1M Functions Invocations, 4 CPU hours/month, 1GB Blob storage, 1M ISR reads, 5K Image transformations, 50K Web Analytics events included.} \newline \textbf{Pro} (\$20/month + additional usage) \newline {\footnotesize \$20/month. 10M Edge Requests, 1TB Data Transfer, 16 CPU hours, 5GB Blob storage, 10M ISR reads, 10K Image transformations included. Overage fees apply.} \newline \textbf{Enterprise} (Custom) \newline {\footnotesize Custom pricing. All usage (Edge Requests, Data Transfer, CPU, Storage, etc.), WAF rules, and build performance are custom configured to client needs. 99.99\% SLA.} \newline & \textbf{Hobby} (Free forever) \newline {\footnotesize 1M Edge Requests, 100GB Data Transfer, 4 CPU hours, 1M Function Invocations, 1M ISR Reads, 1GB Blob, 5K Image Transforms per month.} \newline \textbf{Pro} (\$20/mo + additional usage) \newline {\footnotesize \$20 included usage credit. 10M Edge Requests, 1TB Data Transfer, 2000 Concurrent Sandboxes. Then pay-as-you-go for resources.} \newline \textbf{Enterprise} (Contact Sales) \newline {\footnotesize Custom limits for all resources. Up to 1,000 WAF rules, 99.99\% SLA, Multi-region compute, managed security rulesets.} \newline \\

\end{longtable}

\vfill
\begin{center}
\footnotesize \textcolor{grey}{Generated by Sentinel AI | Confidentially Distributed}
\end{center}

\end{document}
